Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/evaluation.tex
typo

We obtain routing policy for the backbone network and for the data centers of a large cloud provider. Multiple data centers share this policy. The backbone network connects to the data centers and also has many external BGP neighbors. The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).

@@

From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler. However, construction and minimization of the product graph take the most time.

>>>>

We obtained routing policy for the backbone network and for the data centers of a large cloud provider. Multiple data centers share this policy. The backbone network connects to the data centers and also has many external BGP neighbors. The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).

@@

%From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler. However, construction and minimization of the product graph take the most time.
